Last glacial cycle glacier erosion potential in the Alps

### 2021-01-25 articles/erosion/alps-erosion.tex
Rework the results. Oups time for meeting.

    The modelled cumulative (time-integrated) glacial erosion potential
    (Fig.~\ref{fig:cumulative}a) varies by several orders of magnitude
    from insignificant to hundred-metres scale erosion
    potential. Its spatial patterns show a very
    strong localization along the Alpine valleys, with local maxima occuring both at
    the Alpine gates where ice flow transited from valley to piedmont glaciers,
    and further up-valley where valley slopes increase.
    There is a genereral tendency for higher cumulative erosion in the
    north-western Alps where the input winter precipitation
    \citep[WorldClim,][Fig.~1h]{Seguinot.etal.2018} is higher and the
    preexisting glacial topography more pronounced.

@@

    The modelled volumic (domain-integrated) glacial erosion rates
    (Fig.~\ref{fig:cumulative}b) do not correlate with the modelled total ice
    volume. A comparison between the modelled ice volume and the modelled
    volumic erosion rate shows no single relation between these two quantities, except
    for the onset and termination of the glacial cycle were ice volume is low
    and sliding processes unlikely to be captured by the model resolution.
    Instead, erosion is modelled to be higher by a factor 3 to 10 during
    periods of glacier retreat, than during periods of glacier advance
    (Fig.~\ref{fig:evolution}).

@@

    A closer look at the Rhine Glacier, one of the paleo-ice sheet's largest
    outlets, reveals a spatial migration of the modelled high erosion rates.
    During glacier advance and stages of extensive glaciation, the modelled
    erosion rates are moderate and restricted to low elevations, while the
    most interior parts of the Alps \citep[modelled to be
    largely-cold-based][Fig.~6c]{Seguinot.etal.2018}, experience insignificant
    erosion rates (Fig.~\ref{fig:transects}a and~d). The modelled erosion
    rates both increase and propagate inwards during periods of glacier
    retreat (Fig.~\ref{fig:transects}b, c and~d).

    These results can be generalized to the entire model domain by using
    (present-day) bedrock altitude as a proxy for along-flow distance
    (Fig.~\ref{fig:hypsogram}). Periods of modelled increasing and maximum ice
    volume corresponds to local modelled erosion rate minima, with significant
    erosion rates restricted to lower elevations. On the other hand, periods of
    modelled decreased ice volume (and area) correspond to higher local
    modelled erosion rates and a shift of significant erosion rates to
    higher-elevation areas (Fig.~\ref{fig:hypsogram}).

@@

@@

>>>>

    The modelled cumulative (time-integrated) glacial erosion potential
    (Fig.~\ref{fig:cumulative}a) varies by several orders of magnitude
    from insignificant to hundred-metres-scale erosion potential. Its spatial
    patterns show a very strong localization along the Alpine valleys, with
    local maxima occurring both at
    the Alpine gates where ice flow transited from valley to piedmont glaciers,
    and further upstream where the valley slopes increase. While mountain
    cirques are poorly captured by the model horizontal resolution, high
    cumulative erosion potential also occur near the valley heads.
    There is a general tendency for higher cumulative erosion in the
    north-western Alps where the input winter precipitation
    \citep[WorldClim,][Fig.~1h]{Seguinot.etal.2018} is higher and the
    glacial relief more pronounced in the input topography.

@@

    The modelled volumetric (domain-integrated) glacial erosion rates
    do no systematically correlate with the modelled total ice volume
    (Fig.~\ref{fig:cumulative}b). Except for the onset and termination of the
    glacial cycle were ice volume is low and sliding processes unlikely to be
    captured by the model resolution, a comparison between the modelled ice
    volume and the modelled volumetric erosion rate shows no single relation
    between these two quantities (Fig.~\ref{fig:evolution}). After significant
    ice volume has been reached, there is a slight tendency for slower erosion
    during periods of extensive glaciation (Fig.~\ref{fig:evolution}). However,
    the domain-integrated erosion rate is modelled to be consistently higher
    (by a factor 2 to 10) during periods of decreasing ice volume, than during
    periods of increasing ice volume (Fig.~\ref{fig:evolution}).

@@

    A closer look at the Rhine Glacier, one of the paleo-ice sheet's largest
    outlets, reveals a spatial migration of the modelled high erosion rates.
    During stages of glacier advance and maximum extension, erosion is modelled
    to be moderate and restricted the lower parts of the catchment, while much
    the intra-montane Alps \citep[modelled to be largely
    cold-based,][Fig.~6c]{Seguinot.etal.2018}, are modelled to experience
    insignificant erosion (Fig.~\ref{fig:transects}a and~d). The modelled
    erosion rates both increase and propagate inwards during periods of glacier
    retreat (Fig.~\ref{fig:transects}b, c and~d).

    The results found on the Rhine Glacier catchment can be generalized to the
    entire model domain by using (present-day) bedrock altitude as a proxy for
    along-flow distance (Fig.~\ref{fig:hypsogram}). Thus more generally,
    periods of modelled increasing and maximum ice volume corresponds to lower
    values for elevation-aggregated erosion rates, with significant erosion
    restricted to lower elevations. On the opposite, periods of modelled
    decreased ice volume correspond to higher local modelled erosion rates and
    more extensive rapid erosion into higher-elevation areas
    (Fig.~\ref{fig:hypsogram}).

@@

    \note{I have not yet reworked the discussion.}

@@

    \note{I still need to develop the conclusions.}
